Accreditation Thoughts

### 2019-09-11 JHDNotes.tex
Added refereences to SA

\font\manual=manfnt
\def\dbend{{\manual\char127}}
\def\eqq{{\buildrel?\over=}}
\def\C{\mathbf{ C}}
\def\N{\mathbf{ N}}
\def\Q{\mathbf{ Q}}
\def\R{\mathbf{ R}}
\def\Z{\mathbf{Z}}
\def\F{\mathbf{F}}
\def\softO{\tilde{\cal O}}
\def\O{{\cal O}}
%\def\N{{\bf N}}
%\def\Q{{\bf Q}}
%\def\R{{\bf R}}
%\def\Z{{\bf Z}}
\def\action#1{\hfil\rlap{\bf#1}\break}
\def\pcite#1{[#1]}
\def\Res{\mathop{\rm Res}\nolimits}
\def\r#1#2{``#1''$\rightarrow$``#2''}
\documentclass{article}
\bibliographystyle{alphaurl}
\usepackage[hyphens]{url}
%\usepackage{enumitem}
\usepackage{pdfpages}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage{combelow}
\usepackage[show]{ed}
\usepackage{graphicx}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{notation}{Notation}
\newtheorem{example}{Example}
\newtheorem{problem}{Problem}
\def\decision#1{\par{\bf #1}}
\pagestyle{empty}
\begin{document}
\author{Notes by J.H.Davenport}
\title{Accreditation Thoughts}
\date{11 September 2019}
\maketitle
Note \url{https://hbr.org/2019/08/every-computer-science-degree-should-require-a-course-in-cybersecurity}
\section{Possible Questions for Paul to ask Seoul 8+6}
\begin{enumerate}
\item[0.]By CyberSecurity we include what might be called ``Information Security, IT Security etc.''
\item Is there any CyberSecurity in your professional requirements currently?
\item  Do you have plans to change this??
\item Are there any specific detailed requirements
\item Is there any quantification of how much CyberSecurity there should be?
\item Any other comments.
\end{enumerate}

\section{Publishing Venues}
\begin{description}
\item[IT Now]Being pursued, let by TomP.
\item[CEP]A UK focused conference (not necessarily a bad thing).
\item[\qquad11 October 2019]Deadline for abstracts
\item[\qquad18 October 2019]Deadline for full papers
\item[SIGCSE 2020]Main papers are closed, but there may be posters.
\item[ITiCSE]See \url{https://iticse.acm.org/ITiCSE2020/} --- apparently no dates.
\item[Koli]2019 closed 5 August. Presumbaly 2020 will be similar.
\item[Others]??
\end{description}
\end{document}
\section{}
\begin{description}
\item[Q]
\item[A]
\item[Q]
\item[A]
\end{description}

>>>>

\font\manual=manfnt
\def\dbend{{\manual\char127}}
\def\eqq{{\buildrel?\over=}}
\def\C{\mathbf{ C}}
\def\N{\mathbf{ N}}
\def\Q{\mathbf{ Q}}
\def\R{\mathbf{ R}}
\def\Z{\mathbf{Z}}
\def\F{\mathbf{F}}
\def\softO{\tilde{\cal O}}
\def\O{{\cal O}}
%\def\N{{\bf N}}
%\def\Q{{\bf Q}}
%\def\R{{\bf R}}
%\def\Z{{\bf Z}}
\def\action#1{\hfil\rlap{\bf#1}\break}
\def\pcite#1{[#1]}
\def\Res{\mathop{\rm Res}\nolimits}
\def\r#1#2{``#1''$\rightarrow$``#2''}
\documentclass{article}
\bibliographystyle{alphaurl}
\usepackage[hyphens]{url}
%\usepackage{enumitem}
\usepackage{pdfpages}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage{combelow}
\usepackage[show]{ed}
\usepackage{graphicx}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{notation}{Notation}
\newtheorem{example}{Example}
\newtheorem{problem}{Problem}
\def\decision#1{\par{\bf #1}}
\pagestyle{empty}
\begin{document}
\author{Notes by J.H.Davenport}
\title{Accreditation Thoughts}
\date{11 September 2019}
\maketitle
Note \url{https://hbr.org/2019/08/every-computer-science-degree-should-require-a-course-in-cybersecurity}
\section{Possible Questions for Paul to ask Seoul 8+6}
\begin{enumerate}
\item[0.]By CyberSecurity we include what might be called ``Information Security, IT Security etc.'', in fact security aspects of Computing as characterised in footnote 1 of Appendix D.
\item Is there any CyberSecurity in your professional requirements currently?
\item  Do you have plans to change this??
\item Are there any specific detailed requirements
\item Is there any quantification of how much CyberSecurity there should be?
\item Any other comments.
\end{enumerate}
NB: bottom of age 3 reads ``taking into account all relevant technical, legal, social, cultural, economic, and environmental issues and respecting the need for sustainability'' --- in the light of GDPR, this would seem to imply a certain amount of CyberSecurity!
\section{Publishing Venues}
\begin{description}
\item[IT Now]Being pursued, let by TomP.
\item[CEP]A UK focused conference (not necessarily a bad thing).
\item[\qquad11 October 2019]Deadline for abstracts
\item[\qquad18 October 2019]Deadline for full papers
\item[SIGCSE 2020]Main papers are closed, but there may be posters.
\item[ITiCSE]See \url{https://iticse.acm.org/ITiCSE2020/} --- apparently no dates.
\item[Koli]2019 closed 5 August. Presumbaly 2020 will be similar.
\item[Others]??
\end{description}
\end{document}
\section{}
\begin{description}
\item[Q]
\item[A]
\item[Q]
\item[A]
\end{description}
